---
title: "Smith College Mountain Neighbmorhood"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(
  message = FALSE, warning = FALSE, fig.width = 16/2, fig.height = 9/2
)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
library(tidyverse)
library(fivethirtyeight)
library(leaflet)
library(sf)
library(maps)
library(tidycensus)
library(tmaptools)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
House <- c('Cutter','Ziskind','Capen','Gillett','Lamont','Talbot','Nothrop')
Residents <- c('76','77','73','80','83','80','80')
MOUNTAIN_NEIGHBORHOOD <- data.frame(House, Residents)


ggplot(data=MOUNTAIN_NEIGHBORHOOD, mapping=aes(x=House, y=Residents))+
  geom_col()


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
